Midwest Political Science Association

### 2023-03-25 presentations/2023-04-16_mpsa/index.qmd
Quarto-ify the project

---
title: "MPSA 2023 proposal" 
date: "October 6, 2022"
author:
  - name: Andrew Heiss
    email: aheiss@gsu.edu
    orcid: 0000-0002-3948-3914
    affiliations: 
      - id: ays
        name: Georgia State University
        department: Andrew Young School of Policy Studies
        city: Atlanta
        region: GA
    attributes:
      corresponding: true
  - name: Meng Ye
    email: mye2@gsu.edu
    affiliations:
      - ref: ays
format:
  html: default
  docx: default
  pdf: default
---

# Title

@@

# Brief Overview

@@

# Keywords

@@

# Abstract

>>>>

---
title: "Midwest Political Science Association"
date: 2023-04-16
toc: true
abstract: |
  Annual conference of the Midwest Political Science Association (MPSA); Chicago
abstract-title: "Location"
published-title: "Presented"
page-layout: full
---

## Presentation

Slides will be embedded here.

## Proposal

### Title

@@

### Brief Overview

@@

### Keywords

@@

### Abstract
